From Freebase to Wikidata: The Great Migration

### 2015-10-17 paper.tex
section 7

The largest gains for the migration can be achieved
by extending the mapping to more Freebase topics.
A~possible way of realizing this is to create a~user interface%
---possibly leveraging elements of gamification---%
that would allow users to create new Wikidata items for a~suggested topic
or to add a~mapping for them to an existing Wikidata item.
In order to suggest interesting topics to add to Wikidata,
we could rank the not mapped yet topics per number of incoming links
from already mapped topics and filter less interesting types like ISBNs.
Another area for improvement is to upload high quality datasets using a~bot,
like the reviewed facts or some sets for external IDs,
in order to speed up the integration of Freebase content into Wikidata.
We have already started to upload simple reviewed facts about humans
like birth date, death place or gender using a~bot.
We have also begun to import labels that are in Freebase and are absent from Wikidata.
In the 17.2M~Freebase labels for mapped topics, only 0.9M, \emph{i.e.}, 5\%, are missing in Wikidata.

Concluding, in a~fairly short amount of time, we have been able
to provide to the Wikidata community more than\linebreak 14M~new Wikidata statements
using a~novel customizable and generalizable software solution called Primary Sources Tool
that is well integrated into the Wikidata user interface.
The effort needed to map two fairly different knowledge bases has also been a~good occasion
to highlight the difficulty of having good metrics to measure the size
and in consequence the ``value'' of such collaborative knowledge bases.
We envision that this project now with Freebase, and for even more datasets in the future,
will facilitate to increase the completeness of Wikidata.

>>>>

The largest gains for the migration can be achieved
by extending the mapping to more Freebase topics.
A~possible way of realizing this is to create a~user interface%
---possibly leveraging elements of gamification---%
that would allow users to create new Wikidata items for a~suggested topic
or to add a~mapping for them to an existing Wikidata item.
In order to suggest interesting topics to add to Wikidata,
we could rank the topics that are not mapped yet by the number of incoming links
from already mapped topics and filter less interesting types like ISBNs.

Another area for improvement is to upload high quality datasets using a~bot,
like the reviewed facts or some sets for external IDs,
in order to speed up the integration of Freebase content into Wikidata.
We have already started to upload simple reviewed facts about humans
like birth date, death place or gender using a~bot.
We have also started to import labels that are in Freebase and are absent from Wikidata.
In the 17.2~million Freebase labels for mapped topics,
only 0.9~million, \emph{i.e.}, 5\%, are missing in Wikidata.

Concluding, in a~fairly short amount of time, we have been able
to provide to the Wikidata community more than\linebreak 14~million new Wikidata statements
using a~customizable and generalizable approach, consisting of data preparation scripts
and the Primary Sources Tool,
which is well integrated into the Wikidata user interface.
The effort needed to map two fairly different knowledge bases has also been a~good occasion
to highlight the difficulty of having good metrics to measure the size of knowledge bases
in a meaningful way, 
and, in consequence, the ``value'' of such collaborative knowledge bases and the datasets added to them.
We hope that with the help of the Primary Sources Tool and
the Freebase dataset, and in future also other datasets,
will increase the completeness and accuracy of Wikidata.
